Parallel multi-objective optimization using co-evolutionary islands with overlapping search space

### 2016-12-18 hpmoon-coor.tex
New papers for the state of the art
Please @fergunet check them out.

%Introduction should start in the same way as the abstract. And
%starting with something that is not really applicable here, talking
%about general parallel evolutionary algorithms, is even worse - JJ
Different approaches have been used to parallelize Evolutionary
Algorithms (EAs), as each individual can be considered as an
independent unit \citep{Alba13parallel}. Classic methods, such as the
global parallel EAs (Master-Slave), or the spatially structured
algorithms (Island model or Cellular EAs) have been applied
successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these
approaches \citep{Luna15Survey} need to deal with a whole solution set
called Pareto Front (PFs). This imply to use different distribution
and sharing mechanisms, as there exist a tension between the speedup
achievable from parallelization and the need to globally recombine the
results to accurately identify the PF
\citep{Branke04Parallelizingcone}.

@@

>>>>

%Introduction should start in the same way as the abstract. And
%starting with something that is not really applicable here, talking
%about general parallel evolutionary algorithms, is even worse.
% Right way (IMNSHO)
% 1. Multiobjective problems are
% 2. They usually require a good amount of computation → parallel
% distributed
% 3. One way to solve them is to use MOEAs _because_ they can be
% easily parallelized
% 4. But the easy paralellization is not necessarily efficient.
% 5. We have proposed the HPMOON (or whatever) technique to improve
% it. In paper (whatever) we proved that (whatever)
% 6. In this paper we will be proving whatever - JJ
Different approaches have been used to parallelize Evolutionary
Algorithms (EAs), as each individual can be considered as an
independent unit \citep{Alba13parallel}. Classic methods, such as the
global parallel EAs (Master-Slave), or the spatially structured
algorithms (Island model or Cellular EAs) have been applied
successfully in the past \citep{Folino03cellular,Alba02Parallelism}.
In the case of Multi-Objective Evolutionary Algorithms (MOEAs), these
approaches \citep{Luna15Survey} need to deal with a whole solution set
called Pareto Front (PF). This imply to use different distribution
and sharing mechanisms, as there exist a tension between the speedup
achievable from parallelization and the need to globally recombine the
results to accurately identify the PF
\citep{Branke04Parallelizingcone}.

@@

% Parallel multiobjective optimization is the theme. And there are
% papers that do that. Please include them in the state of the art:
% dennis2003parallel (added to bibliography).
